Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2015-10-19 patchy-selection-paper-for-PLoS.tex
final whatnot for submission

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Species often encounter, and adapt to, 
many patches of similar environmental conditions across their range. 
Such adaptation can occur through convergent evolution 
if different alleles arise in different patches, 
or through the spread of shared alleles by migration
acting to synchronize adaptation across the species.
The tension between the two reflects 
the constraint imposed on evolution by the underlying genetic architecture 
versus how effectively selection and geographic isolation 
act to inhibit the geographic spread of locally adapted alleles.
This paper studies the balance between these two routes to adaptation 
in a model of continuous environments with patchy selection pressures.
We address the following questions: 
How long does it take for a novel allele to appear in a
patch where it is locally adapted through mutation?
Or, through migration from another, already adapted patch?
Which is more likely to occur, as a function of distance between the patches?
What population genetic signal is left by the spread of migrant alleles?
To answer these questions we examine the family structure 
underlying migration--selection equilibrium
surrounding an already adapted patch,
treating those rare families that reach new patches
as spatial branching processes.
A main result is that locally adapted alleles in different patches
are likely to be of independent origin
if the distance between the patches is larger than
$(\sigma/s_m)\log(Cs_m/\mu)$, 
where $\sigma$ is the dispersal distance, 
$s_m$ is the selective disadvantage of these alleles between patches,
$\mu$ is the mutation rate, 
and $C$ depends on the probability of establishment and patch geometry.
This provides a way to understand the role of geographic separation between patches 
in promoting convergent adaptation and the genomic signals it leaves behind.
We illustrate these ideas using the convergent evolution of cryptic coloration in the rock pocket mouse, \textit{Chaetodipus intermedius}, as an empirical example.

@@

First we briefly describe the simulations we used for illustration and validation
(the \texttt{R} code used is provided as a supplement).
We simulated forward-time dynamics of the number of alleles of each type in a rectangular grid (either one- or two-dimensional) of demes with fixed size $N$.
Each generation, each individual independently chose to reproduce or not with a probability $r$ depending on her type and location in the grid;
locally beneficial alleles were more likely to reproduce.
Each extant individual then either remained in the same location with probability $1-m$
or else migrated a random number of steps 
in a uniformly chosen cardinal direction; 
for most simulations $m=0.2$ and
the probability of migrating $k$ steps was proportional to $2^{-k}$ for $1\le k \le 5$.
In 2D, diagonal steps were also used.
This gave us values of $\sigma=0.95$ deme spacings in 1D
and $\sigma=0.74$ in 2D.
\linelabel{rr:sim_details}
Once migrants were distributed, each deme was uniformly resampled back down to $N$ individuals.
(Although we described the simulation in terms of individuals,
we kept track only of total numbers in an equivalent way.)

@@

Here we describe how to solve \eqref{eqn:radial_eqfreq_diffeq} exactly in one dimension,

@@

@@

\textbf{Parameter values used in estimates of mean time to adaptation by mutation of figure~\ref{fig:sim_times}.}
All simulations also used a linear grid of 501 demes with a patch of 99 demes in the center, 
the migration model described in \nameref{ss:simulations},
$\mu=10^{-5}$, and $s_p=.0023$ (calculated as the growth rate as described in the text).
$T_\text{adapt}$ is the mean time until 100 $B$ alleles were present in the patch,
and $p_\text{adapted}$ is the proportion of the simulations that adapted by the 25,000 generations.
The simulation began with no $B$ alleles.

\subsection*{S1 Table}
\label{stab:migration_params}

@@

\textbf{Parameter values used in estimates of mean time to adaptation by migration of figure~\ref{fig:sim_times}.}
All simulations also used a linear grid of 501 demes with two patches of 99 demes each,
separated by $R$ demes in the center;
the migration model described in \nameref{ss:simulations},
$\mu=10^{-5}$, and $s_p=.0023$ (calculated as the growth rate as described in the text).
$T_\text{adapt}$ is the mean time until 100 $B$ alleles were present in the patch,
and $p_\text{adapted}$ is the proportion of the simulations that adapted by the 25,000 generations.
At the start of the simulation, one patch was initialized with a frequency of 0.8 $B$ alleles, which were absent elsewhere.

@@

\subsection*{Text S1}

@@

% \bibliography{standing_patches_refs}
\begin{thebibliography}{68}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Aldous(1985)]{aldous1985exchangeability}
D.~J. Aldous.
\newblock Exchangeability and related topics.
\newblock In \emph{École d'été de probabilités de {S}aint-{F}lour,
  {XIII}---1983}, volume 1117 of \emph{Lecture Notes in Math.}, pages 1--198.
  Springer, Berlin, 1985.
\newblock URL
  \url{http://www.springerlink.com/content/c31v17440871210x/fulltext.pdf}.

\bibitem[Allred and Beck(1963)]{allred1963range}
D.~M. Allred and D.~E. Beck.
\newblock Range of movement and dispersal of some rodents at the {Nevada}
  atomic test site.
\newblock \emph{Journal of Mammalogy}, 44\penalty0 (2):\penalty0 pp. 190--200,
  1963.
\newblock ISSN 00222372.
\newblock URL \url{http://www.jstor.org/stable/1377452}.

\bibitem[Arendt and Reznick(2008)]{Arendt:08}
J.~Arendt and D.~Reznick.
\newblock Convergence and parallelism reconsidered: what have we learned about
  the genetics of adaptation?
\newblock \emph{Trends Ecol Evol}, 23\penalty0 (1):\penalty0 26--32, Jan. 2008.
\newblock \doi{10.1016/j.tree.2007.09.011}.

\bibitem[Barton(1979)]{barton1979geneflow}
N.~Barton.
\newblock Gene flow past a cline.
\newblock \emph{Heredity}, 43\penalty0 (3):\penalty0 333--339, Dec. 1979.
\newblock ISSN 0018-067X.
\newblock URL \url{http://dx.doi.org/10.1038/hdy.1979.86}.

\bibitem[Barton(1987)]{barton1987establishment}
N.~H. Barton.
\newblock The probability of establishment of an advantageous mutant in a
  subdivided population.
\newblock \emph{Genetics Research}, 50\penalty0 (1):\penalty0 35--40, 1987.
\newblock \doi{10.1017/S0016672300023314}.
\newblock URL \url{http://dx.doi.org/10.1017/S0016672300023314}.

\bibitem[Barton(2000)]{barton2000genetic}
N.~H. Barton.
\newblock Genetic hitchhiking.
\newblock \emph{Philos Trans R Soc Lond B Biol Sci}, 355\penalty0
  (1403):\penalty0 1553--1562, Nov. 2000.
\newblock \doi{10.1098/rstb.2000.0716}.
\newblock URL \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC1692896/}.

\bibitem[Barton et~al.(2013)Barton, Etheridge, Kelleher, and
  Véber]{barton2013genetic}
N.~H. Barton, A.~M. Etheridge, J.~Kelleher, and A.~Véber.
\newblock Genetic hitchhiking in spatially extended populations.
\newblock \emph{Theoretical Population Biology}, \penalty0 (0):\penalty0 --,
  2013.
\newblock ISSN 0040-5809.
\newblock \doi{10.1016/j.tpb.2012.12.001}.
\newblock URL
  \url{http://www.sciencedirect.com/science/article/pii/S0040580912001359}.

\bibitem[Benson(1933)]{benson1933concealing}
S.~B. Benson.
\newblock \emph{Concealing coloration among some desert rodents of the
  southwestern United States}.
\newblock Number v. 40 in University of California publications in zoology.
  University of California Press, 1933.
\newblock URL \url{http://books.google.com/books?id=Lis-AQAAIAAJ}.

\bibitem[Borodin and Salminen(2002)]{borodin2002handbook}
A.~N. Borodin and P.~Salminen.
\newblock \emph{Handbook of Brownian motion: facts and formulae}.
\newblock Springer, 2002.

\bibitem[Cantrell and Cosner(1989)]{cantrell1989diffusive}
R.~S. Cantrell and C.~Cosner.
\newblock Diffusive logistic equations with indefinite weights: population
  models in disrupted environments.
\newblock \emph{Proceedings of the Royal Society of Edinburgh, Section: A
  Mathematics}, 112\penalty0 (3-4):\penalty0 293--318, 0 1989.
\newblock ISSN 1473-7124.
\newblock \doi{10.1017/S030821050001876X}.
\newblock URL \url{http://journals.cambridge.org/article_S030821050001876X}.

\bibitem[Cantrell and Cosner(1991)]{cantrell1991diffusive}
R.~S. Cantrell and C.~Cosner.
\newblock Diffusive logistic equations with indefinite weights: population
  models in disrupted environments. {II}.
\newblock \emph{SIAM J. Math. Anal.}, 22\penalty0 (4):\penalty0 1043--1064,
  1991.
\newblock ISSN 0036-1410.
\newblock \doi{10.1137/0522068}.
\newblock URL \url{http://dx.doi.org/10.1137/0522068}.

\bibitem[Censky et~al.(1998)Censky, Hodge, and Dudley]{censky1998overwater}
E.~J. Censky, K.~Hodge, and J.~Dudley.
\newblock Over-water dispersal of lizards due to hurricanes.
\newblock \emph{Nature}, 395\penalty0 (6702):\penalty0 556--556, Oct. 1998.
\newblock ISSN 00280836.
\newblock URL \url{http://dx.doi.org/10.1038/26886}.

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Species often encounter, and adapt to, 
many patches of similar environmental conditions across their range. 
Such adaptation can occur through convergent evolution 
if different alleles arise in different patches, 
or through the spread of shared alleles by migration
acting to synchronize adaptation across the species.
The tension between the two reflects 
the constraint imposed on evolution by the underlying genetic architecture 
versus how effectively selection and geographic isolation 
act to inhibit the geographic spread of locally adapted alleles.
This paper studies the balance between these two routes to adaptation 
in a model of continuous environments with patchy selection pressures.
We address the following questions: 
How long does it take for a novel allele to appear in a
patch where it is locally adapted through mutation?
Or, through migration from another, already adapted patch?
Which is more likely to occur, as a function of distance between the patches?
What population genetic signal is left by the spread of migrant alleles?
To answer these questions we examine the family structure 
underlying migration--selection equilibrium
surrounding an already adapted patch,
treating those rare families that reach new patches
as spatial branching processes.
A main result is that patches further apart than a critical distance will
likely evolve independent locally adapted alleles;
this distance is proportional to the spatial scale of selection
($\sigma/\sqrt{s_m}$, where $\sigma$ is the dispersal distance and
$s_m$ is the selective disadvantage of these alleles between patches),
and depends linearly on $\log(s_m/\mu)$, where $\mu$ is the mutation rate.
This provides a way to understand the role of geographic separation between patches 
in promoting convergent adaptation and the genomic signals it leaves behind.
We illustrate these ideas using the convergent evolution of cryptic coloration in the rock pocket mouse, \textit{Chaetodipus intermedius}, as an empirical example.

@@

First we briefly describe the simulations we used for illustration and validation
(the \texttt{R} code used is provided in S1 Scripts and at \url{http://github.com/petrelharp/spatial_selection}).
We simulated forward-time dynamics of the number of alleles of each type in a rectangular grid (either one- or two-dimensional) of demes with fixed size $N$.
Each generation, each individual independently chose to reproduce or not with a probability $r$ depending on her type and location in the grid;
locally beneficial alleles were more likely to reproduce.
Each extant individual then either remained in the same location with probability $1-m$
or else migrated a random number of steps 
in a uniformly chosen cardinal direction; 
for most simulations $m=0.2$ and
the probability of migrating $k$ steps was proportional to $2^{-k}$ for $1\le k \le 5$.
In 2D, diagonal steps were also used.
This gave us values of $\sigma=0.95$ deme spacings in 1D
and $\sigma=0.74$ in 2D.
\linelabel{rr:sim_details}
Once migrants were distributed, each deme was uniformly resampled back down to $N$ individuals.
(Although we described the simulation in terms of individuals,
we kept track only of total numbers in an equivalent way.)

@@

Description of how to solve \eqref{eqn:radial_eqfreq_diffeq} exactly in one dimension,

@@

\subsection*{S1 Scripts}

\textbf{Scripts used in producing this manuscript.}
These can also be found at \url{http://github.com/petrelharp/spatial_selection}.

@@

% % latex table generated in R 3.1.2 by xtable 1.7-4 package
% % Wed Dec 17 14:13:09 2014
% % \begin{table}[ht]
% \begin{center}
% {\tiny
% \begin{tabular}{|rrrrrrr||rrrrrrr|}
%   \hline
% $\mu$ & $\rho$ & $s_p$ & $s_m$ & $T_\text{adapt}$ & $p_\text{adapted}$ & n & $\mu$ & $\rho$ & $s_p$ & $s_m$ & $T_\text{adapt}$ & $p_\text{adapted}$ & n \\ 
%   \hline
% 1e-05 & 25 & 0.01 & -0.10 & 19630 & 0.06 & 100 & 1e-05 & 600 & 0.01 & -0.10 & 1082 & 1.00 & 40 \\ 
%   1e-05 & 25 & 0.01 & -0.01 & 15533 & 0.55 & 100 & 1e-05 & 600 & 0.01 & -0.01 & 924 & 1.00 & 40 \\ 
%   1e-05 & 25 & 0.01 & -0.00 & 14353 & 0.72 & 100 & 1e-05 & 600 & 0.01 & -0.01 & 828 & 1.00 & 40 \\ 
%   1e-05 & 25 & 0.01 & -0.00 & 13282 & 0.74 & 100 & 1e-05 & 600 & 0.01 & -0.00 & 846 & 1.00 & 40 \\ 
%   1e-05 & 50 & 0.01 & -0.10 & 11587 & 0.33 & 40 & 1e-05 & 600 & 0.01 & -0.00 & 966 & 1.00 & 40 \\ 
%   1e-05 & 50 & 0.01 & -0.10 & 11586 & 0.38 & 40 & 1e-05 & 800 & 0.01 & -0.10 & 802 & 1.00 & 40 \\ 
%   1e-05 & 50 & 0.01 & -0.01 & 9419 & 0.88 & 40 & 1e-05 & 800 & 0.01 & -0.10 & 1182 & 1.00 & 40 \\ 
%   1e-05 & 50 & 0.01 & -0.01 & 8848 & 0.82 & 40 & 1e-05 & 800 & 0.01 & -0.01 & 846 & 1.00 & 40 \\ 
%   1e-05 & 50 & 0.01 & -0.00 & 6529 & 0.95 & 40 & 1e-05 & 800 & 0.01 & -0.01 & 607 & 1.00 & 40 \\ 
%   1e-05 & 50 & 0.01 & -0.00 & 9986 & 0.90 & 40 & 1e-05 & 800 & 0.01 & -0.00 & 646 & 1.00 & 40 \\ 
%   1e-05 & 100 & 0.01 & -0.10 & 7425 & 0.91 & 316 & 1e-05 & 800 & 0.01 & -0.00 & 507 & 1.00 & 40 \\ 
%   1e-06 & 100 & 0.01 & -0.10 & 21010 & 0.23 & 217 & 1e-05 & 1000 & 0.01 & -0.10 & 615 & 1.00 & 256 \\ 
%   1e-05 & 100 & 0.01 & -0.03 & 6036 & 0.98 & 195 & 2.4e-06 & 1000 & 0.01 & -0.10 & 5309 & 0.96 & 257 \\ 
%   1e-06 & 100 & 0.01 & -0.03 & 19859 & 0.31 & 194 & 1e-05 & 1000 & 0.01 & -0.03 & 523 & 1.00 & 194 \\ 
%   1e-05 & 100 & 0.01 & -0.01 & 5408 & 0.98 & 315 & 1e-06 & 1000 & 0.01 & -0.03 & 6425 & 0.95 & 195 \\ 
%   1e-06 & 100 & 0.01 & -0.01 & 20606 & 0.28 & 216 & 1e-05 & 1000 & 0.01 & -0.01 & 449 & 1.00 & 254 \\ 
%   1e-05 & 100 & 0.01 & -0.00 & 4745 & 0.99 & 195 & 2.4e-06 & 1000 & 0.01 & -0.01 & 4806 & 0.96 & 256 \\ 
%   1e-06 & 100 & 0.01 & -0.00 & 19564 & 0.33 & 195 & 1e-05 & 1000 & 0.01 & -0.00 & 460 & 1.00 & 193 \\ 
%   1e-05 & 100 & 0.01 & -0.00 & 4894 & 0.99 & 315 & 1e-06 & 1000 & 0.01 & -0.00 & 5203 & 0.98 & 194 \\ 
%   1e-06 & 100 & 0.01 & -0.00 & 19417 & 0.33 & 216 & 1e-05 & 1000 & 0.01 & -0.00 & 444 & 1.00 & 255 \\ 
%   1e-05 & 100 & 0.01 & -0.00 & 4940 & 0.99 & 316 & 2.4e-06 & 1000 & 0.01 & -0.00 & 4037 & 1.00 & 257 \\ 
%   1e-06 & 100 & 0.01 & -0.00 & 18025 & 0.40 & 217 & 1e-05 & 1000 & 0.01 & -0.00 & 404 & 1.00 & 216 \\ 
%   1e-05 & 200 & 0.01 & -0.10 & 4296 & 0.97 & 40 & 1e-06 & 1000 & 0.01 & -0.00 & 4567 & 1.00 & 216 \\ 
%   1e-05 & 200 & 0.01 & -0.10 & 3736 & 1.00 & 40 & 1e-05 & 1200 & 0.01 & -0.10 & 501 & 1.00 & 40 \\ 
%   1e-05 & 200 & 0.01 & -0.01 & 2943 & 1.00 & 40 & 1e-05 & 1200 & 0.01 & -0.10 & 460 & 1.00 & 40 \\ 
%   1e-05 & 200 & 0.01 & -0.01 & 2402 & 1.00 & 40 & 1e-05 & 1200 & 0.01 & -0.01 & 336 & 1.00 & 40 \\ 
%   1e-05 & 200 & 0.01 & -0.00 & 1899 & 1.00 & 40 & 1e-05 & 1200 & 0.01 & -0.01 & 431 & 1.00 & 40 \\ 
%   1e-05 & 200 & 0.01 & -0.00 & 1992 & 1.00 & 40 & 1e-05 & 1200 & 0.01 & -0.00 & 390 & 1.00 & 40 \\ 
%   1e-05 & 400 & 0.01 & -0.10 & 1740 & 1.00 & 100 & 1e-05 & 1200 & 0.01 & -0.00 & 372 & 1.00 & 40 \\ 
%   1e-05 & 400 & 0.01 & -0.01 & 1471 & 1.00 & 100 & 1e-05 & 1600 & 0.01 & -0.10 & 299 & 1.00 & 100 \\ 
%   1e-05 & 400 & 0.01 & -0.00 & 1446 & 1.00 & 100 & 1e-05 & 1600 & 0.01 & -0.01 & 462 & 0.99 & 100 \\ 
%   1e-05 & 400 & 0.01 & -0.00 & 1224 & 1.00 & 100 & 1e-05 & 1600 & 0.01 & -0.00 & 241 & 1.00 & 100 \\ 
%   1e-05 & 600 & 0.01 & -0.10 & 1276 & 1.00 & 40 & 1e-05 & 1600 & 0.01 & -0.00 & 274 & 1.00 & 100 \\ 
%    \hline
% \end{tabular}
% }
%\caption
{
    \textbf{Parameter values used in estimates of mean time to adaptation by mutation of figure~\ref{fig:sim_times}.}
            All simulations also used a linear grid of 501 demes with a patch of 99 demes in the center, 
            the migration model described in \nameref{ss:simulations},
            $\mu=10^{-5}$, and $s_p=.0023$ (calculated as the growth rate as described in the text).
            $T_\text{adapt}$ is the mean time until 100 $B$ alleles were present in the patch,
            and $p_\text{adapted}$ is the proportion of the simulations that adapted by the 25,000 generations.
            The simulation began with no $B$ alleles.
% \label{stab:mutation_params}
% \end{center}
%\end{table}

\subsection*{S2 Table}
 \label{stab:migration_params}

@@

% latex table generated in R 3.1.2 by xtable 1.7-4 package
% Wed Dec 17 14:14:44 2014
%\begin{table}[ht]
%\begin{center}
%{\tiny
%\begin{tabular}{|rrrrrrr||rrrrrrr|}
%  \hline
%R & $\rho$ & $s_p$ & $s_m$ & $T_\text{adapt}$ & $p_\text{adapted}$ & n & R & $\rho$ & $s_p$ & $s_m$ & $T_\text{adapt}$ & $p_\text{adapted}$ & n \\ 
%  \hline
%100 & 100 & 0.01 & -1e-01 & 24975 & 0.00 & 300 & 60 & 1000 & 0.01 & -3e-02 & 22224 & 0.21 & 200 \\ 
%  10 & 100 & 0.01 & -1e-01 & 24975 & 0.00 & 40 & 100 & 1000 & 0.01 & -1e-02 & 18098 & 0.55 & 299 \\ 
%  120 & 100 & 0.01 & -1e-01 & 24975 & 0.00 & 295 & 10 & 1000 & 0.01 & -1e-02 & 14 & 1.00 & 100 \\ 
%  160 & 100 & 0.01 & -1e-01 & 24975 & 0.00 & 40 & 120 & 1000 & 0.01 & -1e-02 & 23242 & 0.14 & 297 \\ 
%  20 & 100 & 0.01 & -1e-01 & 24975 & 0.00 & 40 & 160 & 1000 & 0.01 & -1e-02 & 24762 & 0.01 & 100 \\ 
%  40 & 100 & 0.01 & -1e-01 & 24975 & 0.00 & 40 & 20 & 1000 & 0.01 & -1e-02 & 136 & 1.00 & 100 \\ 
%  60 & 100 & 0.01 & -1e-01 & 24975 & 0.00 & 300 & 40 & 1000 & 0.01 & -1e-02 & 874 & 1.00 & 99 \\ 
%  80 & 100 & 0.01 & -1e-01 & 24975 & 0.00 & 40 & 60 & 1000 & 0.01 & -1e-02 & 3485 & 1.00 & 300 \\ 
%  100 & 100 & 0.01 & -3e-02 & 24975 & 0.00 & 200 & 80 & 1000 & 0.01 & -1e-02 & 9204 & 0.96 & 100 \\ 
%  120 & 100 & 0.01 & -3e-02 & 24975 & 0.00 & 199 & 100 & 1000 & 0.01 & -3e-03 & 4168 & 1.00 & 200 \\ 
%  60 & 100 & 0.01 & -3e-02 & 24903 & 0.01 & 200 & 120 & 1000 & 0.01 & -3e-03 & 6304 & 1.00 & 200 \\ 
%  100 & 100 & 0.01 & -1e-02 & 24354 & 0.04 & 300 & 60 & 1000 & 0.01 & -3e-03 & 1273 & 1.00 & 199 \\ 
%  10 & 100 & 0.01 & -1e-02 & 1705 & 0.95 & 40 & 100 & 1000 & 0.01 & -1e-03 & 2813 & 1.00 & 299 \\ 
%  120 & 100 & 0.01 & -1e-02 & 24802 & 0.01 & 299 & 10 & 1000 & 0.01 & -1e-03 & 12 & 1.00 & 100 \\ 
%  160 & 100 & 0.01 & -1e-02 & 24975 & 0.00 & 40 & 120 & 1000 & 0.01 & -1e-03 & 4002 & 1.00 & 300 \\ 
%  20 & 100 & 0.01 & -1e-02 & 3601 & 0.95 & 40 & 160 & 1000 & 0.01 & -1e-03 & 7386 & 1.00 & 100 \\ 
%  40 & 100 & 0.01 & -1e-02 & 9463 & 0.88 & 40 & 20 & 1000 & 0.01 & -1e-03 & 121 & 1.00 & 100 \\ 
%  60 & 100 & 0.01 & -1e-02 & 18674 & 0.45 & 299 & 40 & 1000 & 0.01 & -1e-03 & 507 & 1.00 & 100 \\ 
%  80 & 100 & 0.01 & -1e-02 & 23899 & 0.12 & 40 & 60 & 1000 & 0.01 & -1e-03 & 1115 & 1.00 & 300 \\ 
%  100 & 100 & 0.01 & -3e-03 & 14601 & 0.80 & 200 & 80 & 1000 & 0.01 & -1e-03 & 1941 & 1.00 & 100 \\ 
%  120 & 100 & 0.01 & -3e-03 & 18645 & 0.53 & 199 & 100 & 1000 & 0.01 & -1e-04 & 2528 & 1.00 & 300 \\ 
%  60 & 100 & 0.01 & -3e-03 & 5424 & 0.98 & 200 & 10 & 1000 & 0.01 & -1e-04 & 11 & 1.00 & 99 \\ 
%  100 & 100 & 0.01 & -1e-03 & 8992 & 0.96 & 299 & 120 & 1000 & 0.01 & -1e-04 & 3590 & 1.00 & 298 \\ 
%  10 & 100 & 0.01 & -1e-03 & 522 & 1.00 & 40 & 160 & 1000 & 0.01 & -1e-04 & 5648 & 1.00 & 100 \\ 
%  120 & 100 & 0.01 & -1e-03 & 11375 & 0.93 & 300 & 20 & 1000 & 0.01 & -1e-04 & 122 & 1.00 & 100 \\ 
%  160 & 100 & 0.01 & -1e-03 & 16930 & 0.68 & 40 & 40 & 1000 & 0.01 & -1e-04 & 498 & 1.00 & 100 \\ 
%  20 & 100 & 0.01 & -1e-03 & 1518 & 0.97 & 40 & 60 & 1000 & 0.01 & -1e-04 & 1051 & 1.00 & 298 \\ 
%  40 & 100 & 0.01 & -1e-03 & 2234 & 1.00 & 40 & 80 & 1000 & 0.01 & -1e-04 & 1796 & 1.00 & 100 \\ 
%  60 & 100 & 0.01 & -1e-03 & 4277 & 0.98 & 300 & 10 & 4000 & 0.01 & -1e-01 & 0 & 1.00 & 20 \\ 
%  80 & 100 & 0.01 & -1e-03 & 5328 & 1.00 & 40 & 160 & 4000 & 0.01 & -1e-01 & 24975 & 0.00 & 20 \\ 
%  100 & 100 & 0.01 & -1e-04 & 6867 & 0.99 & 299 & 20 & 4000 & 0.01 & -1e-01 & 4406 & 1.00 & 20 \\ 
%  10 & 100 & 0.01 & -1e-04 & 461 & 1.00 & 40 & 40 & 4000 & 0.01 & -1e-01 & 24975 & 0.00 & 20 \\ 
%  120 & 100 & 0.01 & -1e-04 & 9347 & 0.99 & 300 & 80 & 4000 & 0.01 & -1e-01 & 24975 & 0.00 & 20 \\ 
%  160 & 100 & 0.01 & -1e-04 & 12731 & 0.90 & 40 & 10 & 4000 & 0.01 & -1e-02 & 3746 & 0.85 & 20 \\ 
%  20 & 100 & 0.01 & -1e-04 & 860 & 1.00 & 40 & 160 & 4000 & 0.01 & -1e-02 & 24975 & 0.00 & 20 \\ 
%  40 & 100 & 0.01 & -1e-04 & 2031 & 1.00 & 40 & 20 & 4000 & 0.01 & -1e-02 & 58 & 1.00 & 20 \\ 
%  60 & 100 & 0.01 & -1e-04 & 3529 & 0.99 & 300 & 40 & 4000 & 0.01 & -1e-02 & 362 & 1.00 & 20 \\ 
%  80 & 100 & 0.01 & -1e-04 & 4839 & 1.00 & 40 & 80 & 4000 & 0.01 & -1e-02 & 4025 & 1.00 & 20 \\ 
%  100 & 1000 & 0.01 & -1e-01 & 24975 & 0.00 & 300 & 10 & 4000 & 0.01 & -1e-03 & 6244 & 0.75 & 20 \\ 
%  10 & 1000 & 0.01 & -1e-01 & 1004 & 0.99 & 100 & 160 & 4000 & 0.01 & -1e-03 & 4399 & 1.00 & 20 \\ 
%  120 & 1000 & 0.01 & -1e-01 & 24975 & 0.00 & 298 & 20 & 4000 & 0.01 & -1e-03 & 52 & 1.00 & 20 \\ 
%  160 & 1000 & 0.01 & -1e-01 & 24975 & 0.00 & 100 & 40 & 4000 & 0.01 & -1e-03 & 281 & 1.00 & 20 \\ 
%  20 & 1000 & 0.01 & -1e-01 & 18403 & 0.42 & 100 & 80 & 4000 & 0.01 & -1e-03 & 1209 & 1.00 & 20 \\ 
%  40 & 1000 & 0.01 & -1e-01 & 24965 & 0.00 & 100 & 10 & 4000 & 0.01 & -1e-04 & 3746 & 0.85 & 20 \\ 
%  60 & 1000 & 0.01 & -1e-01 & 24975 & 0.00 & 300 & 160 & 4000 & 0.01 & -1e-04 & 3798 & 1.00 & 20 \\ 
%  80 & 1000 & 0.01 & -1e-01 & 24975 & 0.00 & 100 & 20 & 4000 & 0.01 & -1e-04 & 52 & 1.00 & 20 \\ 
%  100 & 1000 & 0.01 & -3e-02 & 24975 & 0.00 & 200 & 40 & 4000 & 0.01 & -1e-04 & 279 & 1.00 & 20 \\ 
%  120 & 1000 & 0.01 & -3e-02 & 24975 & 0.00 & 200 & 80 & 4000 & 0.01 & -1e-04 & 1039 & 1.00 & 20 \\ 
%   \hline
%\end{tabular}
%}
%%\caption
{
    \textbf{Parameter values used in estimates of mean time to adaptation by migration of figure~\ref{fig:sim_times}.}
            All simulations also used a linear grid of 501 demes with two patches of 99 demes each,
            separated by $R$ demes in the center;
            the migration model described in \nameref{ss:simulations},
            $\mu=10^{-5}$, and $s_p=.0023$ (calculated as the growth rate as described in the text).
            $T_\text{adapt}$ is the mean time until 100 $B$ alleles were present in the patch,
            and $p_\text{adapted}$ is the proportion of the simulations that adapted by the 25,000 generations.
            At the start of the simulation, one patch was initialized with a frequency of 0.8 $B$ alleles, which were absent elsewhere.
% \label{stab:migration_params}
% \end{center}
%\end{table}

@@

@@

% \bibliography{standing_patches_refs}
\begin{thebibliography}{10}

\bibitem{stern2013genetic}
Stern DL.
\newblock The genetic causes of convergent evolution.
\newblock Nat Rev Genet. 2013 Nov;14(11):751--764.
\newblock Available from: \url{http://www.ncbi.nlm.nih.gov/pubmed/24105273}.

\bibitem{zhen2012parallel}
Zhen Y, Aardema ML, Medina EM, Schumer M, Andolfatto P.
\newblock Parallel Molecular Evolution in an Herbivore Community.
\newblock Science. 2012;337(6102):1634--1637.
\newblock Available from:
  \url{http://www.sciencemag.org/content/337/6102/1634.abstract}.

\bibitem{martin2013repeated}
Martin A, Orgogozo V.
\newblock The loci of repeated evolution: a catalog of genetic hotspots of
  phenotypic variation.
\newblock Evolution. 2013;67(5):1235--1250.
\newblock Available from: \url{http://dx.doi.org/10.1111/evo.12081}.

\bibitem{Arendt:08}
Arendt J, Reznick D.
\newblock Convergence and parallelism reconsidered: what have we learned about
  the genetics of adaptation?
\newblock Trends Ecol Evol. 2008 Jan;23(1):26--32.

\bibitem{softsweepsII}
Pennings PS, Hermisson J.
\newblock Soft Sweeps {II} - Molecular Population Genetics of Adaptation from
  Recurrent Mutation or Migration.
\newblock Mol Biol Evol. 2006;p. msj117.
\newblock Available from:
  \url{http://mbe.oxfordjournals.org/cgi/content/abstract/msj117v1}.

\bibitem{ralph2010parallel}
Ralph P, Coop G.
\newblock Parallel Adaptation: One or Many Waves of Advance of an Advantageous
  Allele?
\newblock Genetics. 2010;186(2):647--668.
\newblock Available from:
  \url{http://www.genetics.org/cgi/content/abstract/186/2/647}.

\bibitem{orr2001sieve}
Orr HA, Betancourt AJ.
\newblock Haldane's sieve and adaptation from the standing genetic variation.
\newblock Genetics. 2001 Feb;157(2):875--884.
\newblock Available from: \url{http://www.ncbi.nlm.nih.gov/pubmed/11157004}.

\bibitem{softsweepsI}
Hermisson J, Pennings PS.
\newblock Soft sweeps: molecular population genetics of adaptation from
  standing genetic variation.
\newblock Genetics. 2005 Apr;169(4):2335--2352.
\newblock Available from: \url{http://www.ncbi.nlm.nih.gov/pubmed/15716498}.

\bibitem{slatkin1973geneflow}
Slatkin M.
\newblock Gene Flow and Selection in a Cline.
\newblock Genetics. 1973;75(4):733--756.
\newblock Available from:
  \url{http://www.genetics.org/cgi/content/abstract/75/4/733}.

\bibitem{kruckeberg1951intraspecific}
Kruckeberg AR.
\newblock Intraspecific Variability in the Response of Certain Native Plant
  Species to Serpentine Soil.
\newblock American Journal of Botany. 1951;38(6):pp. 408--419.
\newblock Available from: \url{http://www.jstor.org/stable/2438248}.

\bibitem{macnair1991evolution}
Macnair MR.
\newblock Why the evolution of resistance to anthropogenic toxins normally
  involves major gene changes: the limits to natural selection.
\newblock Genetica. 1991;84(3):213--219.
\newblock Available from: \url{http://dx.doi.org/10.1007/BF00127250}.

\bibitem{schat1996identical}
Schat H, Vooijs R, Kuiper E.
\newblock Identical Major Gene Loci for Heavy Metal Tolerances that Have
  Independently Evolved in Different Local Populations and Subspecies of
  \textit{{Silene} vulgaris}.
\newblock Evolution. 1996;50(5):pp. 1888--1895.
\newblock Available from: \url{http://www.jstor.org/stable/2410747}.

\bibitem{turner2010serpentine}
Turner TL, Bourne EC, Von~Wettberg EJ, Hu TT, Nuzhdin SV.
\newblock Population resequencing reveals local adaptation of
  \textit{{Arabidopsis} lyrata} to serpentine soils.
\newblock Nat Genet. 2010 Jan;42(3):260--3.
\newblock Available from: \url{http://www.ncbi.nlm.nih.gov/pubmed/20101244}.

\bibitem{benson1933concealing}
Benson SB.
\newblock Concealing coloration among some desert rodents of the southwestern
  United States.
\newblock No. v. 40 in University of California publications in zoology.
  University of California Press; 1933.
\newblock Available from: \url{http://books.google.com/books?id=Lis-AQAAIAAJ}.

\bibitem{DiceBlossom1937}
Dice LR, Blossom PM.
\newblock Studies of Mammalian Ecology in Southwestern North America With
  Special Attention to the Colors of Desert Mammals.
\newblock Carnegie Institution; 1937.

\bibitem{kaufman1974adaptive}
Kaufman DW.
\newblock Adaptive Coloration in \textit{{Peromyscus} polionotus}: Experimental
  Selection by Owls.
\newblock Journal of Mammalogy. 1974;55(2):pp. 271--283.
\newblock Available from: \url{http://www.jstor.org/stable/1378997}.

\bibitem{hoekstra2003different}
Hoekstra HE, Nachman MW.
\newblock Different genes underlie adaptive melanism in different populations
  of rock pocket mice.
\newblock Mol Ecol. 2003 May;12:1185--1194.
\newblock Available from:
  \url{http://www3.interscience.wiley.com/journal/118890526/abstract}.
